An MCM Paper Made by Team 1234567

### 2025-01-23 论文/PAPER.tex
修改了论文
更新论文
叶徐俊更新了论文
合并了PAPER和PAPER模板

% 本模板不需要填写年份，以当前电脑时间自动生成
% 请在以下的方括号中填写队伍控制号
\usepackage[1234567]{easymcm}  % 载入 EasyMCM 模板文件
\problem{A}  % 请在此处填写题号
\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
%\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包

@@

% 文档开始
\begin{document}

% 此处填写摘要内容
\begin{abstract}
	Hello, MCM.

@@

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
    % \vspace{5pt}
    % \textbf{Keywords}: MATLAB, mathematics, LaTeX.

\end{abstract}

@@

Two major problems are discussed in this paper, which are:
\begin{itemize}
    \item Doing the first thing.
    \item Doing the second thing.
\end{itemize}

\subsection{Literature Review}
A literatrue\cite{1} say something about this problem ...

@@

\section{Preparation of the Models}
\subsection{Assumptions}

\subsection{Notations}
The primary notations used in this paper are listed in Table \ref{tb:notation}.

@@

\section{The Models}
\subsection{Model 1}
\subsubsection{Details about Model 1}
The detail can be described by equation \eqref{eq:heat}:
\begin{equation}\label{eq:heat}
\frac{\partial u}{\partial t} - a^2 \left( \frac{\partial^2 u}{\partial x^2} + \frac{\partial^2 u}{\partial y^2} + \frac{\partial^2 u}{\partial z^2} \right) = f(x, y, z, t)
\end{equation}

\subsection{Model 2}
\subsubsection{Conclusion of Model 2}
The results are shown in Figure \ref{fig:result}, where $t$ denotes the time in seconds, and $c$ refers to the concentration of water in the boiler.

@@

\clearpage
\subsubsection{Commetary on Model 2}
The instance of long and wide tables are shown in Table \ref{tb:longtable}.

@@

\section{Strengths and Weaknesses}
\subsection{Strengths}
\begin{itemize}
    \item First one...
    \item Second one ...
\end{itemize}

@@

>>>>

% 本模板不需要填写年份，以当前电脑时间自动生成
% 请在以下的方括号中填写队伍控制号
\usepackage[2506135]{easymcm}  % 载入 EasyMCM 模板文件
\problem{C}  % 请在此处填写题号
\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
%\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包
\usepackage{amsmath}

@@

% 文档开始
\newtheorem{keywords}{Keywords}
\begin{document}

% 此处填写摘要内容
\begin{abstract}

@@

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
    % \vspace{5pt}
    % \textbf{Keywords}: MATLAB, mathematics, LaTeX.
\begin{keywords}
\end{keywords}
\end{abstract}

@@

Two major problems are discussed in this paper, which are:
\begin{itemize}
    \item Doing the first thing.
    \item Doing the second thing.\\doing\\    doing11

\end{itemize}

\subsection{Restatement of Problem}
A literatrue\cite{1} say something about this problem ...

@@

\section{Assumptions}

\section{Notations}
The primary notations used in this paper are listed in Table \ref{tb:notation}.

@@

\section{Data Preprocessing}
\subsection{Basic Data Preprocessing}
\subsection{Data Mining}
\section{Task1:}
\subsubsection{Details about Model 1}
The detail can be described by equation \eqref{eq1}:\autoref{eq1}:
%带标签的方程
\begin{equation}\label{eq1}
\alpha+\beta=\gamma
\end{equation}
%不带标签的方程
\[
\alpha+\beta=\gamma
\]
$$\alpha$$

%长等式
\begin{equation}\label{eq2}
	\begin{split}
	&A+B+C+D+E+F\\
	&=G+Q+W+E+R+T+Y\\
	&=A+S+D+F+G+H+J
	\end{split}
\end{equation}
%分段方程
\begin{equation}\label{eq3}
	F(x)=
	\begin{cases}
		0&,\text{if $x<0$}\\
		x+1&,\text{if $x>0$}\\
		1&,\text{otherwise}
			\end{cases}
\end{equation}

\section{Task2:}
\subsection{Conclusion of Model 2}
The results are shown in Figure \ref{fig:result}, where $t$ denotes the time in seconds, and $c$ refers to the concentration of water in the boiler.

@@

\clearpage
\subsection{Commetary on Model 2}
The instance of long and wide tables are shown in Table \ref{tb:longtable}.

@@

\section{Task3}

\section{Task4}

\section{Sensitivity Analysis}

\section{Model Evaluation}
\subsection{Strengths}
\begin{itemize}
    \item First one...
    \item Second one ...
\end{itemize}

@@

\section{Conclusion}
